Political Support in the United States

### 2024-03-17 paper/paper.qmd
Update paper.qmd

>>>>

## Males are less likely to support Biden than Females, women most likely to vote for Biden.

Based on the analysis of Figure 1, located under 2.3 Measurement, we can infer that males (represented by 1) exhibit a lower propensity to support Biden compared to females (represented by 2). Throughout most of the race, 1 consistently has fewer votes than 2. Specifically, women are identified as the demographic most inclined to vote for Biden, indicating a notable gender disparity in political preferences favoring the Biden candidacy.
